\documentclass[letterpaper]{article} 
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{array}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage[version=4]{mhchem}
\usepackage{stmaryrd}
\usepackage[dvipsnames]{xcolor}
\colorlet{LightRubineRed}{RubineRed!70}
\colorlet{Mycolor1}{green!10!orange}
\definecolor{Mycolor2}{HTML}{00F9DE}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{capt-of}
\usepackage{lipsum}
\usepackage{fancyvrb}
\usepackage{tabularx}
\usepackage{listings}
\usepackage[export]{adjustbox}
\graphicspath{ {./images/} }
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{float}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{float}
\usepackage[margin=0.7in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{capt-of}
\usepackage{tcolorbox}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{float}
\usepackage{listings}
\usepackage{hyperref} 
\usepackage{xcolor} % For custom colors
\lstset{
	language=Python,                % Choose the language (e.g., Python, C, R)
	basicstyle=\ttfamily\small, % Font size and type
	keywordstyle=\color{blue},  % Keywords color
	commentstyle=\color{gray},  % Comments color
	stringstyle=\color{red},    % String color
	numbers=left,               % Line numbers
	numberstyle=\tiny\color{gray}, % Line number style
	stepnumber=1,               % Numbering step
	breaklines=true,            % Auto line break
	backgroundcolor=\color{black!5}, % Light gray background
	frame=single,               % Frame around the code
}
\usepackage{float}
\usepackage[]{amsthm} %lets us use \begin{proof}
\usepackage[]{amssymb} %gives us the character \varnothing

	\title{Homework 7, MATH 4061}
	\author{Zongyi Liu}
	\date{Fri, Oct 17, 2025}
	\begin{document}
		\maketitle
		
		\section{Question 1}
		\textbf{Uniformly and Lipschitz continuous functions}
		
		Consider the functions $f, g: \mathbb{R}_{\geq 0} \rightarrow \mathbb{R}$ given by $f(x)=x^{2}$ and $g(x)=\sqrt{x}$. Show that $f$ is continuous but not uniformly continuous, and show that $g$ is uniformly continuous but not Lipschitz continuous.
		
		
	
		
		\textbf{Answer}
		
		\clearpage
	
	
	\section{Question 2}
	\textbf{Continuity}
	
	Let $f: \mathbb{R}^{n} \rightarrow \mathbb{R}, g: \mathbb{R}^{n} \rightarrow \mathbb{R}, \lambda \in \mathbb{R}$. Show that the functions $f+g$, and $\lambda f$ are also continuous.
	
\textbf{Answer}

\clearpage


	\section{Question 3}
\textbf{Monotone functions}

Let $f: \mathbb{R} \rightarrow \mathbb{R}$ be a monotonically increasing function. Show that the set of points where $f$ is discontinuous is at most countable.


\textbf{Answer}

\clearpage


\section{Question 4}
\textbf{Sequences of continuous functions}

Let $\left(f_{n}\right)_{n \in \mathbb{N}}$ be a sequence of continuous functions on the interval $[0,1]$ and suppose that there exists a function $f:[0,1] \rightarrow \mathbb{R}$ such that

$$
\lim _{n \rightarrow \infty} f_{n}(x)=f(x)
$$

for all $x \in[0,1]$. Is $f$ also continuous?

\textbf{Answer}

\clearpage

	\section{Question 5}
	
\textbf{Convex functions}

Let $[a, b] \subset \mathbb{R}$ be a non-empty interval. A function $f:[a, b] \rightarrow \mathbb{R}$ is called convex if

$$
f(\lambda x+(1-\lambda) y) \leq \lambda f(x)+(1-\lambda) f(y)
$$

for all $x, y \in[a, b]$ and $\lambda \in[0,1]$. Show that $f$ is continuous. Moreover, given a continuous function $g:[a, b] \rightarrow \mathbb{R}$ which satisfies

$$
g\left(\frac{1}{2} x+\frac{1}{2} y\right) \leq \frac{1}{2} g(x)+\frac{1}{2} g(y)
$$

for all $x, y \in[a, b]$, show that $g$ is convex.

\textbf{Answer}

\clearpage

\section{Question 6}

\textbf{Constant functions}

Suppose that $f: \mathbb{R} \rightarrow \mathbb{R}$ satisfies $|f(x)-f(y)| \leq(x-y)^{2}$ for all $x, y \in \mathbb{R}$. Show that $f$ is constant.


\textbf{Answer}

\clearpage

\section{Question 7}

\textbf{Path-connected sets}

Let ($X, d$) be a metric space and let $A \subseteq X$ be path-connected. Show that $A$ is also connected.


\textbf{Answer}

\clearpage

\section{Question 8}

\textbf{Topologist's Sine Curve}

Show that the set

$$
T=\{(x, \sin (1 / x)): x \in(0,1]\} \cup(\{0\} \times[-1,1]) \subset \mathbb{R}^{2} .
$$

is connected but not path-connected.

\textbf{Answer}

\clearpage
	
	
	\end{document}
